%-------------------------------------------------------------------------------
%  SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%  CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Chief Data Engineer} % Job title
  {Fortescue {\color{awesome-nephritis} Zero} \acvHeaderSocialSep {\fontsize{10pt}{1em}\bodyfont\upshape\color{futurepurple} Elysia Battery Intelligence}} % Organization
  {Oxford, UK} % Location
  {Aug. 2025 --- Current} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {\textbf{cloud data platform lead}, owning architecture and delivery for the next-generation Elysia cloud platform and products}
    \item {Leading \textbf{cross-functional} execution across product, data science, battery analytics, cell modelling, and systems engineering to ship platform capabilities at scale}
    \item {Managing a \textbf{multidisciplinary} team of data engineers, DevOps, platform engineers, solutions architects, and sysops engineers}
    \item {Managing \textbf{ISO27001 and SOC2} compliance strategy and execution, embedding controls, evidence capture, and continuous monitoring}
    \item {Set platform \textbf{strategy and visioning} for scalability, reliability, performance, and cost efficiency}
    \item {Aligned stakeholders and customers on roadmap, priorities, and operating model for platform adoption}
    \end{cvitems}
  }

  \cventry
  {Principal Data Engineer} % Job title
  {Fortescue {\color{awesome-nephritis} Zero} \acvHeaderSocialSep {\fontsize{10pt}{1em}\bodyfont\upshape\color{futurepurple} Elysia Battery Intelligence}} % Organization
  {Oxford, UK} % Location
  {Feb. 2024 --- Jul. 2025} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Lead the cloud data engineering team, driving scalable and efficient solutions}
    \item {Key player in \textbf{Fortescue -- Jaguar Land Rover} multi-year collaboration, overseeing automation, data pipelines, and cloud infrastructure}
    \item {Design, optimize, and manage scalable cloud infrastructure, ETL/ELT pipelines, and the \textbf{Elysia tech stack} to enable advanced analytics and \textbf{automated solutions} for automotive and stationary storage applications.}
      % \item {Design, deploy, and manage scalable, automated cloud infrastructure and ETL/ELT pipelines, optimizing data processing, reliability, security, and resiliency}
      % \item {Manage and evolve the Elysia software/tech stack to support advanced analytics and applications}
      % \item {Partner with battery scientists to develop cloud-based, automated solutions for automotive and stationary storage applications}
    \item {Lead technical efforts in \textbf{ISO 27001} certification efforts, ensuring \textbf{compliance} and \textbf{security} best practices}
    \item {Deliver rapid technical solutions for unique, high-impact challenges}
    \item {Act as a \textbf{customer-facing technical leader}, supporting commercial, product, and business initiatives}
    \end{cvitems}
  }

  \cventry
  {Senior Data Scientist} % Job title
  {Fortescue {\color{awesome-nephritis} Zero} \acvHeaderSocialSep {\fontsize{10pt}{1em}\bodyfont\upshape\color{futurepurple} Elysia Battery Intelligence}} % Organization
  {Oxford, UK} % Location
  {Jan. 2024 --- Feb. 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Co-led the design/development of the Elysia software/tech stack, laying the foundation for advanced analytics and performance optimization.}
      % \item {Played a key role in migrating the DevOps pipeline to GitHub, enhancing efficiency, collaboration, and version control.}
    \item {Co-designed and implemented CI/CD pipelines, streamlining software deployment and integration.}
    \item {Led the migration to Infrastructure as Code (IaC) using Terraform, improving scalability and manageability.}
      % \item {Delivered rapid technical solutions to complex, high-impact challenges, ensuring timely delivery and performance.}
      % \item {Provided technical expertise in customer-facing roles, supporting commercial, product, and business initiatives.}
    \end{cvitems}
  }

  \cventry
  {Research Associate} % Job title
  {University of Oxford \acvHeaderSocialSep {\fontsize{10pt}{1em}\bodyfont\upshape\color{futurepurple} Department of Materials}} % Organization
  {Oxford, United Kingdom} % Location
  {Jan. 2022 - Jan. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Established the group’s computational infrastructure, enabling advanced simulations and research.}
    \item {Improved open-source software developed through the CATMAT project, enhancing functionality and usability for the wider community.}
    \item {Discovered sulfur redox in an understudied family of cathode materials, unlocking potential for higher energy density in next-generation batteries, accelerated through \textbf{AI/ML} techniques.}
    \item {Collaborated on oxygen redox projects, using \textbf{AI/ML} to identify the role of voids in voltage degradation and capacity fade.}
    \item {Managed and optimized the group’s computational resources at high-performance computing (HPC) centers, ensuring efficient resource utilization for research needs.}
    \end{cvitems}
  }

  \cventry
  {Research Associate} % Job title
  {University of Bath \acvHeaderSocialSep {\fontsize{10pt}{1em}\bodyfont\upshape\color{futurepurple} Department of Chemistry}} % Organization
  {Bath, United Kingdom} % Location
  {June 2020 - Dec. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item{Developed software and data pipelines for automated, large-scale materials discovery in energy storage.}
    \item{Developed workflows for the large-scale screening of millions of structures to identify thermodynamically stable structures, facilitating materials discovery and configurational entropy calculation.}
    \item{Brought in expertise in task orchestration and automation using AiiDA, helping team members improve efficiency with streamlined workflows.}
    \end{cvitems}
  }

  \cventry
  {Marie Skłodowska-Curie Postdoctoral Fellow} % Job title
  {Central European Institute of Technology \acvHeaderSocialSep {\fontsize{10pt}{1em}\bodyfont\upshape\color{futurepurple} Masaryk University}} % Organization
  {Brno, Czechia} % Location
  {Apr. 2017 - Apr. 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Principal Investigator of COMPSTORE project}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {DGAPA Postodoctoral Fellow} % Job title
  {National Autonomous University of Mexico \acvHeaderSocialSep {\fontsize{10pt}{1em}\bodyfont\upshape\color{futurepurple} Institute of Chemistry}} % Organization
  {Mexico City, Mexico} % Location
  {Mar. 2016 - Apr. 2017} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Implementing the biogas upgrading project}
    \end{cvitems}
  }

  %---------------------------------------------------------
  %   \cventry
  %     {Undergraduate Internship} % Job title
  %     {Arak Oil refinery} % Organization
  %     {Arak, Iran} % Location
  %     {Jun. 2011 - Dec. 2013} % Date(s)
  %     {
  %       \begin{cvitems} % Description(s) of tasks/responsibilities
  %         \item {Working in different parts of QC lab}
  %       \end{cvitems}
  %     }

  %---------------------------------------------------------
\end{cventries}
% \clearpage
